---
title: "Brandon Moretz's resume"
author: Brandon Moretz
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(tidyverse)
library(ggthemes)
library(glue)
library(readxl)
library(docstring)
library(kableExtra)

library(cowplot)
library(MASS)
library(actuar)
library(evd)
library(mvtnorm)

# Theme Settings

theme.colors <- list(sidebar = "#f7fbff")

theme_set(theme_light())

# Theme Overrides
theme_update(axis.text.x = element_text(size = 10),
             axis.text.y = element_text(size = 10),
             plot.title = element_text(hjust = 0.5, size = 16, face = "bold", color = "darkgreen"),
             axis.title = element_text(face = "bold", size = 12, colour = "steelblue4"),
             plot.subtitle = element_text(face = "bold", size = 8, colour = "darkred"),
             panel.background = element_rect(fill = "transparent"),
             plot.background = element_rect(fill = theme.colors$sidebar, color = NA), # bg of the plot to match the sidebar.
             legend.title = element_text(size = 12, color = "darkred", face = "bold"),
             legend.position = "right", legend.title.align=0.5,
             panel.border = element_rect(linetype = "solid", 
                                         colour = "lightgray"), 
             plot.margin = unit(c( 0.1, 0.1, 0.1, 0.1), "inches"))

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

# Include our parsing / manipulation routines.
source('parsing_functions.R')

# Grab the background info excel file and store it for later.
data.sheet <- "background.xlsx"

```

Aside
================================================================================

```{r}
sigma <- matrix( c(1,.5,.5,1), 2, 2)
x <- data.frame(rmvt(n = 10000, sigma, df = 2, delta = rep(0, nrow(sigma)) )) 

x_cdf <- cbind(pt(x[,1],df=2),pt(x[,2], df=2)) 
z1 <- x_cdf[,1] 
z2 <- x_cdf[,2] 

z1 <- qgev( x_cdf[,1], loc=0.0004, scale=0.0009, shape=-0.3)  
z2 <- qbeta( x_cdf[,2], shape1=4.0, shape2=2.8 )
x <- data.frame(z1,z2)

alpha <- .75

pmain <- ggplot(x, aes(z1,z2)) +
  geom_point(alpha = alpha, col = "darkgrey") +
  stat_density_2d(aes(fill = stat(level), alpha = ..level..), geom = "polygon") +
  labs(x = "", y = "") +
  theme(legend.position = "none",
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        axis.text.x = element_blank(), axis.text.y = element_blank())

xbox <- axis_canvas(pmain, axis = "x") +
  geom_histogram(data = x, aes(z1, y = ..density.., fill = ..count..), size = .2, bins = 50, alpha = alpha) +
  geom_density(data = x, aes(z1), col = "darkgrey", alpha = .55) +
  theme(legend.position = "none")

ybox <- axis_canvas(pmain, axis = "y", coord_flip = T) +
  geom_histogram(data = x, aes(z2, y = ..density.., fill = ..count..), size = .2, bins = 50, alpha = alpha) +
  geom_density(data = x, aes(z2), col = "darkgrey", alpha = .55) +
  coord_flip() +
  theme(legend.position = "none")

suppressWarnings({
  p1 <- insert_xaxis_grob(pmain, xbox, grid::unit(.2, "null"), position = "top")
  p2 <- insert_yaxis_grob(p1, ybox, grid::unit(.2, "null"), position = "right")
})

ggdraw(p2)
```

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> <text style="font-size: 11px">bmoretz@ionicsolutions.net</text>
- <i class="fab fa-linkedin-in"></i> [LinkedIn](https://www.linkedin.com/in/bmoretz/)
- <i class="fa fa-github"></i> [Github](https://github.com/bmoretz)
- <i class="fab fa-stack-overflow"></i> [Stack Overflow](https://stackoverflow.com/users/538272/brandon-moretz)
- <i class="fas fa-rss"></i> [Blog](https://ionicsolutions.net/)
- <i class="fa fa-phone"></i> +1 347-891-2826

- For more information, please contact me via email.


Language Skills {#skills}
--------------------------------------------------------------------------------

```{r}
skill_chart(data.sheet)
```

- Experienced in statistical analysis, statistical learning models, and optimization methods.

- Full experience with next generation sequencing data analysis.

- Highly skilled in R, Bash, Perl, Python, LaTeX


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.



Main
================================================================================

Brandon Moretz {#title}
--------------------------------------------------------------------------------

### Quantitative Development

Please note that this is a *real* resume, and I'm really looking for a PhD
student position at the moment. I made this resume because Yihui asked me
if I'd like to test the **pagedown** package with my resume. If you are
interested in my background and skills, please feel free to contact me.


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_education(data.sheet)
```

Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Head of Development

MSD Capital, L.P.

New York, NY

Dec '19 - Feb '13

**Analytics Platform**

Lead development effort on our in-house proprietary data analytics  and risk system on a team of five.

- Lead development effort on our in-house proprietary data analytics  and risk system on a team of five.
- Presentation layer constructed with WPF/C#, Service-Oriented-Architecture built with WCF/C#, data layer modeled in T-SQL and processed with R packages deployed to the server instance, invoked directly with stored procedures.
- Built a suite of FX hedging and settlement tools to automate our FX process. 
- Constructed the core FX Hedging model in R, which used various metrics of hedging (FMV, Cost, MTM, Fixed, Underlying, Custom Model, etc.) to calculate the target hedge by strategy then aggregate by total currency exposure across the firm.

Technology: R, C#, WPF

**Option Pricing Framework**

- Lead development effort on our in-house proprietary data analytics  and risk system on a team of five.
- Presentation layer constructed with WPF/C#, Service-Oriented-Architecture built with WCF/C#, data layer modeled in T-SQL and processed with R packages deployed to the server instance, invoked directly with stored procedures.
- Built a suite of FX hedging and settlement tools to automate our FX process. Constructed the core FX Hedging model in R, which used various metrics of hedging (FMV, Cost, MTM, Fixed, Underlying, Custom Model, etc.) to calculate the target hedge by strategy then aggregate by total currency exposure across the firm.

Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

### Graduate Research Assistant

Beijing Institute of Genomics, Chinese Academy of Sciences

Beijing, China

2011 - 2014

- Performed computational biology research towards understanding regulation of alternative splicing in human and mouse transcriptome.
- Found EGFR pathway related mutations, aimed to understand the impacts of cancer mutations on EGFR signaling pathway.

### Bioinformatican

My Health Gene Technology Co., Ltd.

Beijing, China

2015 - 2016

- Investigated how cancer cells spread to other parts of the body at the single cell level.

### Visiting Scientist

University of Alabama at Birmingham

AL, USA

2016 - 2018

- Investigated the role of mitochondria in development of cancer.
- Investigated the evolution of genome architecture and its role in important evolutionary events.
- Detected thrombotic thrombocytopenic purpura related mutations in mutiple patients' blood genome.
  


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

### Introduction to R Language for Beginners.

Instructor of R and Data Mining Training Courses at SupStat Inc.

Beijing, China

2014

### Computational Biology and Bioinformatics.

Teaching assistant of GBS CB2-201 courses at UAB

AL, USA

2016 - 2017


Selected Publications and Posters {data-icon=file}
--------------------------------------------------------------------------------

### Genetic and epigenetic signals are found predictive to the distribution of intra-individual divergence of alternative splicing.

Poster for 2013 International Conference of Genomics

Qingdao, China

2014

**Yu L**, Chen B, Zhang Z.

### ESCRT-0 complex modulates Rbf mutant cell survival by regulating Rhomboid endosomal trafficking and EGFR signaling.

J Cell Sci. 2016 May 15;129(10):2075-84.

N/A

2016 

Sheng Z, **Yu L**, Zhang T, Pei X, Li X, Zhang Z and Du W. 
