---
title: "Brandon Moretz's resume"
author: Brandon Moretz
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(tidyverse)
library(ggthemes)
library(glue)
library(readxl)
library(docstring)
library(cowplot)

library(MASS)
library(actuar)
library(evd)
library(mvtnorm)

# Theme Settings

theme.colors <- list(sidebar = "#f7fbff")

theme_set(theme_light())

# Theme Overrides
theme_update(axis.text.x = element_text(size = 10),
             axis.text.y = element_text(size = 10),
             plot.title = element_text(hjust = 0.5, size = 16, face = "bold", color = "darkgreen"),
             axis.title = element_text(face = "bold", size = 12, colour = "steelblue4"),
             plot.subtitle = element_text(face = "bold", size = 8, colour = "darkred"),
             panel.background = element_rect(fill = "transparent"),
             plot.background = element_rect(fill = theme.colors$sidebar, color = NA), # bg of the plot to match the sidebar.
             legend.title = element_text(size = 12, color = "darkred", face = "bold"),
             legend.position = "right", legend.title.align=0.5,
             panel.border = element_rect(linetype = "solid", 
                                         colour = "lightgray"), 
             plot.margin = unit(c( 0.1, 0.1, 0.1, 0.1), "inches"))

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Include our parsing / manipulation routines.
source('parsing_functions.R')

# Grab the background info excel file and store it for later.
data.sheet <- "background.xlsx"

select <- dplyr::select
```

Aside
================================================================================

```{r}
sigma <- matrix( c(1,.5,.5,1), 2, 2)
x <- data.frame(rmvt(n = 10000, sigma, df = 2, delta = rep(0, nrow(sigma)) )) 

x_cdf <- cbind(pt(x[,1],df=2),pt(x[,2], df=2)) 
z1 <- x_cdf[,1] 
z2 <- x_cdf[,2] 

z1 <- qgev( x_cdf[,1], loc=0.0004, scale=0.0009, shape=-0.3)  
z2 <- qbeta( x_cdf[,2], shape1=4.0, shape2=2.8 )
x <- data.frame(z1,z2)

alpha <- .75

pmain <- ggplot(x, aes(z1,z2)) +
  geom_point(alpha = alpha, col = "darkgrey") +
  stat_density_2d(aes(fill = stat(level), alpha = ..level..), geom = "polygon") +
  labs(x = "", y = "") +
  theme(legend.position = "none",
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        axis.text.x = element_blank(), axis.text.y = element_blank())

xbox <- axis_canvas(pmain, axis = "x") +
  geom_histogram(data = x, aes(z1, y = ..density.., fill = ..count..), size = .2, bins = 50, alpha = alpha) +
  geom_density(data = x, aes(z1), col = "darkgrey", alpha = .55) +
  theme(legend.position = "none")

ybox <- axis_canvas(pmain, axis = "y", coord_flip = T) +
  geom_histogram(data = x, aes(z2, y = ..density.., fill = ..count..), size = .2, bins = 50, alpha = alpha) +
  geom_density(data = x, aes(z2), col = "darkgrey", alpha = .55) +
  coord_flip() +
  theme(legend.position = "none")

suppressWarnings({
  p1 <- insert_xaxis_grob(pmain, xbox, grid::unit(.2, "null"), position = "top")
  p2 <- insert_yaxis_grob(p1, ybox, grid::unit(.2, "null"), position = "right")
})

ggdraw(p2)
```

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> <text style="font-size: 11px">bmoretz@ionicsolutions.net</text>
- <i class="fab fa-linkedin-in"></i> [LinkedIn](https://www.linkedin.com/in/bmoretz/)
- <i class="fa fa-github"></i> [Github](https://github.com/bmoretz)
- <i class="fab fa-stack-overflow"></i> [Stack Overflow](https://stackoverflow.com/users/538272/brandon-moretz)
- <i class="fas fa-rss"></i> [Blog](https://ionicsolutions.net/)
- <i class="fa fa-phone"></i> +1 (201) 878-4968

- For more information, please contact me via email.

Language Skills {#skills}
--------------------------------------------------------------------------------

```{r}
skill_chart(data.sheet)
```

- Expert knowledge of the Windows Platform SDK, .NET Framework, Windows Presentation/Communication Foundations.

- Experienced in statistical analysis, statistical learning models, and optimization methods.

- Passion for building scalable, reliable and performant quantitative systems.


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Resume created with the R package [*pagedown*](https://github.com/rstudio/pagedown).


Main
================================================================================

Brandon Moretz {#title}
--------------------------------------------------------------------------------
### Quantitative Development

An experienced software engineering professional with a successful track record working in the investment management industry. Successfully managed teams in a hands-on capacity at all of my previous roles after entering as an individual contributor.

Enjoys solving problems, learning and teaching others. 
 
Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------
```{r}
print_education(data.sheet)
```

Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
print_professional(data.sheet)
```

Professional Development {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
print_certs(data.sheet)
```
